\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-12 paper.tex
code model -> syntactic model

A semantic model \cite{fowler2010domain}, tied closely to the DSL itself, can
fulfill this role. Semantic transformations evolve the model into a
code-oriented model, comparable to the idea of CodeDom. From there on,
syntactic transformations an emit source code. Figure \ref{fig:code-generation}
shows the process that \NAME implements.

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=7mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)  [resource]                                 {DSL};
  \node (sm)   [representation,right=of dsl,align=center] {Semantic\\Model};
  \node (cm)   [representation,right=of sm,align=center]  {Code\\Model};
  \node (code) [resource,right=of cm]        {Code};

@@

After parsing the DSL, it's imported into a semantic model. The minimal type
information present in the initial model allows inferring of the remaining
types. Through a series of semantic transformations, the model evolves from the
functional to a more technical code model. This code model is comparable to a
rich abstract syntax tree (AST) with an extensive set of language constructs.
Syntactic transformations now lower this level of expressiveness according to
the desired platform and language. In the end the code model can be directly
emitted to the target language.

@@

FCF typically looks for patterns in the semantic model and performs model
transformations to change these patterns to a more optimized organization. It
first performs semantic transformations on the semantic model itself and ends
then transforms the semantic model into a code model, encoding the semantics
into technical code constructs.

\subsubsection{Code Model}

The code model is an AST for a virtual, expressive language. It contains
constructs and ideas found in different languages and programming paradigms. No
single existing programming language supports all features as is. Syntactic
transformations therefore morph the unsupported constructs into comparable
constructs supported by the targeted platform and language.

>>>>

A semantic model \cite{fowler2010domain}, tied closely to the DSL itself, can
fulfill this role. Semantic transformations evolve the model into a
syntax-oriented model, comparable to the idea of CodeDom. From there on,
syntactic transformations an emit source code. Figure \ref{fig:code-generation}
shows the process that \NAME implements.

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=7mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)  [resource]                                 {DSL};
  \node (sm)   [representation,right=of dsl,align=center] {Semantic\\Model};
  \node (cm)   [representation,right=of sm,align=center]  {Syntactic\\Model};
  \node (code) [resource,right=of cm]        {Code};

@@

After parsing the DSL, it's imported into a semantic model. The minimal type
information present in the initial model allows inferring of the remaining
types. Through a series of semantic transformations, the model evolves from the
functional to a more technical syntactic model. This model is comparable to a
rich abstract syntax tree (AST) with an extensive set of language constructs.
Syntactic transformations now lower this level of expressiveness according to
the desired platform and language. In the end the syntactic model can be
directly emitted to the target language.

@@

FCF typically looks for patterns in the semantic model and performs model
transformations to change these patterns to a more optimized organization. It
first performs semantic transformations on the semantic model itself and ends
then transforms the semantic model into a syntactic model, encoding the
semantics into technical syntax constructs.

\subsubsection{Syntactic Model}

The syntactic model is an AST for a virtual, expressive language. It contains
constructs and ideas found in different languages and programming paradigms. No
single existing programming language supports all features as is. Syntactic
transformations therefore morph the unsupported constructs into comparable
constructs supported by the targeted platform and language.
